### 2013-03-28 doc/sosp13/evaluation.tex
g
pe

\paragraph{Global memory and communication.} We measure the performance of
\Grappa's global memory and communication layers using a faithful
implementation of the giga updates per second (GUPS) benchmark.
Read-modify-write updates are dispatched at random to a large array. This
benchmark stresses the communication layer of \Grappa separately from the
scheduler, because only a single worker is used per system node.
Figure~\ref{fig:grappa-gups} shows that \Grappa is able to sustain well over a
billion updates per second with 64 nodes. This compares very favorably to
published results~\footnote{\url{http://icl.cs.utk.edu/hpcc/hpcc_results.cgi}}
for other high-end HPC systems.

@@

\begin{figure}[ht]
    \begin{center}
      \begin{tabular}{c|c c c c}
        Benchmark     & Communication & User & Idle & Context Switch \\ \hline
        GUPS          & 6.60  & 42.94   & 47.74 & 2.80 \\
        BFS           & 54.84 & 30.90   & 10.94 & 3.43 \\ 
        Intsort       & 34.28 & 42.00   & 21.31 & 2.47 \\ 
        UTS           & 40.57 & 56.52   &  1.21 & 1.73 \\
        Pagerank      & 76.79 & 20.71   &  0.06 & 2.50 \\
      \end{tabular}
    \end{center}
    \caption{\Grappa\ execution time profile, in percent.}
%bar chart, one set of bars per benchmark, one bar per system. runtime normalized to grappa.
    \label{fig:grappa-profile}
\end{figure}

>>>>

\paragraph{Global memory and communication.} We measure the performance of
\Grappa's global memory and communication layers using a faithful
implementation of the giga updates per second (GUPS) benchmark.
Read-modify-write updates are dispatched at random to a large array. This
benchmark stresses the communication layer of \Grappa separately from the
scheduler, because only a single worker is used per system node.
Figure~\ref{fig:grappa-gups} shows that \Grappa is able to sustain well over a
billion updates per second with 64 nodes. This compares very favorably to
published results~\cite{gups} for other high-end HPC systems.

@@

\begin{figure}[ht]
    \begin{center}
      \begin{tabular}{c|c c c c}
        Benchmark     & Comm & User & Idle & Sched \\ \hline
        GUPS          & 6.60  & 42.94   & 47.74 & 2.80 \\
        BFS           & 54.84 & 30.90   & 10.94 & 3.43 \\ 
        Intsort       & 34.28 & 42.00   & 21.31 & 2.47 \\ 
        UTS           & 40.57 & 56.52   &  1.21 & 1.73 \\
        Pagerank      & 76.79 & 20.71   &  0.06 & 2.50 \\
      \end{tabular}
    \end{center}
    \caption{\Grappa\ execution time profile, in percent.}
%bar chart, one set of bars per benchmark, one bar per system. runtime normalized to grappa.
    \label{fig:grappa-profile}
\end{figure}
